---
title: "Untitled"
output: html_document
---

#  Summary of Bayesian Networks

```{r pressure, echo=TRUE}
####----V. Summary of Bayesian Networks----####
p <- 10
set.seed(50)
myDAG <- randomDAG(p, prob = 0.2)
if (require(Rgraphviz))
{ plot(myDAG, main = "randomDAG(10, prob = 0.2)") }


```
# Generate 10000 samples of the DAG using standard normal error distribution

```{r pressure, echo=TRUE}
#2. Generate 10000 samples of the DAG using standard normal error distribution
n <- 10000
mydataset <- rmvDAG(n, myDAG, errDist = "normal")


```
# Use PC algorithm to learn the causal structure of the dataset.
```{r pressure, echo=TRUE}

#3. Use PC algorithm to learn the causal structure of the dataset.
suffStat <- list(C = cor(mydataset)
, n = nrow(mydataset))
my.pc.fit <- pc(suffStat, indepTest = gaussCItest
, p=ncol(mydataset), alpha = 0.01)
plot(my.pc.fit@graph)

```
# Estimate the causal effects of node 2 on nodes 5,9.
```{r pressure, echo=TRUE}

#4. Estimate the causal effects of node 2 on nodes 5,9.
idaFast(2, c(5,9), cov(mydataset), my.pc.fit@graph)

```
# Find the parent and children set of node 7 using pcSelect (the PC-Simple algorithm)
```{r pressure, echo=TRUE}

#5. Find the parent and children set of node 7 using
# pcSelect (the PC-Simple algorithm)
pcS <- pcSelect(mydataset[,7],mydataset[,-7], alpha = 0.05)
pcS


```
# Find the parent and children set of node 7 using HITON-PC

```{r pressure, echo=TRUE}
#6. Find the parent and children set of node 7 using HITON-PC
HITON.PC.7 <- learn.nbr(data.frame(mydataset),"X7"
, method = "si.hiton.pc", alpha = 0.01)
HITON.PC.7


```
# Learn the Markov blanket of node 7 from data

```{r pressure, echo=TRUE}

#7. Learn the Markov blanket of node 7 from data
MB.X7 <- learn.mb(data.frame(mydataset),"X7"
,method = "iamb", alpha = 0.01)
MB.X7

```
